Experiences with Planning for Natural Language Generation

### 2009-06-01 trunk/Papers/ci-spark/experiments.tex
xtag graphs
figures moved to the right places
using subfig
added modifier runtime picture

\begin{figure}
  \centering
  \includegraphics[width=0.75\columnwidth]{graph-exp1}
  %\includegraphics[width=1\columnwidth]{pic-runtime-modifiers-with-sgplan}
  \caption{Results for the sentence generation domain. The
    horizontal axis represents parameters $(m,n)$ from $(1,1)$ to
    $(10,10)$ in lexicographical order. The vertical axis is the
    runtime in milliseconds.}
  \label{fig:runtimes-crisp}
\end{figure}

@@

The results of this experiment are shown in the graph in
Figure~\ref{fig:runtimes-crisp}.\footnote{All
  runtimes were measured on a Pentium 4 CPU running at 3 GHz. Java programs
  were allowed to ``warm up'', i.e., the planner was run five times and the
  first four measurements discarded to ensure that the JVM had just-in-time
  compiled all relevant bytecode.} The input parameters $(m,n)$ are
plotted in lexicographic order on the horizontal axis, and the runtime
is shown in milliseconds on the vertical axis.\footnote{These times
  were measured on XXX} These results reveal a number of interesting
insights. First, FF significantly outperforms SGPLAN in this domain,
sometimes by a factor of 10 or more.\footnote{Experiments with SGPLAN
  use a pre-release version of SGPLAN, kindly provided to us by
  Chih-Wei Hsu.The release version of SGPLAN 5.2.2 had a bug which
  caused it to crash on some of our problem instances.}  Second, FF's
runtime is dominated by its initial grounding step, in which it
computes the ground instances of all predicates and actions used in
the planning problem in order to avoid unnecessary instantiation
during search.  In particular, the ratio of grounding time to total
runtime is generally above 85\%, and rises to above 99\% at $m=11$,
which is still a relatively small universe for this
application.\footnote{The ``grounding'' time reported here is what FF
  reports as ``time spent: instantiating action templates''.}

@@

\begin{figure}
  \centering

  \caption{Results for the XTAG experiment. The horizontal axis
    represents parameters $(k,n)$ from $(1,1)$ to $(3,10)$ in
    lexicographic order. The vertical axis is runtime in milliseconds.}
  \label{fig:xtag-graph}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{data/modifiers-all}
  \caption{Results for the sentence generation domain. The
    horizontal axis represents parameters $(m,n)$ from $(1,1)$ to
    $(10,10)$ in lexicographical order. The vertical axis is the
    runtime in milliseconds.}
  \label{fig:runtimes-crisp}
\end{figure}

@@

The results of this experiment are shown in the graph in
Figure~\ref{fig:runtimes-crisp}.\footnote{All runtimes in
  Sections~\ref{sec:exper-1:-sent} and \ref{sec:exper-2:-sent-xtag}
  were measured on an AMD Opteron 8220 CPU running at 2.8 GHz, under
  Linux. FF 2.3 and Metric-FF were recompiled as 64-bit binaries. Java
  programs were executed under Java 1.6.0\_13 in 64-bit mode. They
  were allowed to ``warm up'', i.e. the JVM was given the opportunity
  to just-in-time compile the relevant bytecode by running the planner
  three times and discarding the runtimes before taking the actual
  measurements. All runtimes are averaged over three runs of
  the planners.} The input parameters $(m,n)$ are plotted in
lexicographic order on the horizontal axis, and the runtime is shown
in seconds on the vertical axis. These results reveal a number of
interesting insights. First, FF significantly outperforms SGPLAN in
this domain, sometimes by a factor of 10 or more. Second, FF's runtime
is dominated by its initial grounding step, in which it computes the
ground instances of all predicates and actions used in the planning
problem in order to avoid unnecessary instantiation during search.  In
particular, the ratio of grounding time to total runtime is generally
above 85\%, and rises to above 99\% at $m=11$, which is still a
relatively small universe for this application.\footnote{The
  ``grounding'' time reported here is what FF reports as ``time spent:
  instantiating action templates''.}

@@

\begin{figure}[t]
\subfloat[$k=1$]{\includegraphics[width=8cm]{data/xtag-k1.pdf}}
\subfloat[$k=2$]{\includegraphics[width=8cm]{data/xtag-k2.pdf}}
  \caption{Results for the XTAG experiment, at $k=1$ and $k=2$.}
  \label{fig:xtag-graph}
\end{figure}
